Probing the Circumgalactic Medium of Submillimeter Galaxies with QSO Absorption Spectroscopy

### 2016-08-04 SMGI/qph_vla_v4.tex
jxp

\begin{abstract}
Submillimeter galaxies (SMGs) are dusty starbursts in the early universe that may have evolved into massive ellipticals today. Their clustering strength suggests that they inhabit $10^{13}$~\msun\ halos. The physical state of the circumgalactic medium of SMGs carries key information to decode massive galaxy formation yet are unexplored observationally. We exploit QSO absorption spectroscopy to probe the diffuse gas around SMGs.
% 
We first compile a sample of \sqps\ with angular separations less than 35\arcsec\ from \hers\ surveys. We then use the Very Large Array (VLA) to determine the positions of the \hers\ sources. Finally, we use near-infrared spectrographs to determine the redshifts of the five VLA-detected SMGs and optical spectrographs to obtain their QSO absorption spectra. 
%
Our survey yielded three \sqps\ with secure redshift identification for both components. The QSO sightlines probe transverse proper distances between 110 and 200~kpc. We detect strong \HI\ \lya\ absorption with rest-frame equivalent widths $W_{\rm Ly\alpha} = 1.7-2.0$~\AA\ around all three SMGs. One of the \lya\ system shows only 40\% absorption at the line center, so it is clearly optically thin (${\rm log}(N_{\rm HI}) < 17$~\cmsq) and the high $W_{\rm Ly\alpha}$ is due to line-blending. The high equivalent widths and the line center depths of the other two systems are consistent with optically thick absorbers with $18 < {\rm log}(N_{\rm HI}) < 19$~\cmsq. However, neither are convincingly optically thick, because our spectral resolution is insufficient to reveal the damping wings of the \lya\ line and the low-ionization metal lines commonly associated with optically thick absorbers are buried in the \lya\ forest. Compared to the QSOs at $z \sim 2$, our limited sample suggest that SMGs' surrounding media have lower covering fraction of optically thick cool gas. 
\end{abstract}

@@

The first mJy-level submillimeter surveys discovered a population of high-redshift submillimeter-bright galaxies (SMGs), namely, unresolved sources with 850~\um\ flux density ($S_{850}$) greater than 3~mJy \citep{Smail97,Barger98,Hughes98,Eales99}. The SMGs are massive \citep[\ms\ $\sim 10^{11}$~\msun;][]{Hainline11, Michalowski12, Targett12}, metal-rich \citep[$Z \sim Z_\odot$;][]{Swinbank04}, gas-rich \citep[\mg\ $\sim 3\times10^{10}$~\msun;][]{Greve05, Tacconi08, Ivison11}, extreme star-forming systems (SFR $\gtrsim 500$~\msunyr) at a median redshift of $z \sim 2.5$ \citep{Chapman05,Wardlow11,Yun12,Smolcic12}. Two lines of evidence suggest that SMGs inhabit dark matter halos as massive as $\sim$$10^{13}$~\msun: (1) their strong clustering strength estimated from the cross-correlation function between SMGs and 3.6~\um-selected galaxies \citep[\mh $\sim 9\times10^{12}$~\msun; e.g.,][]{Hickox12}, and (2) their high stellar mass and the \ms$-$\mh\ relation from abundance matching \citep[\mh~$= 6\times10^{12}$~\msun\ for \ms~$= 10^{11}$~\msun\ at $z = 2$; e.g.,][]{Behroozi10}.

It is imperative to know how long this intense star formation would last. For $10^{13}$~\msun\ halos at $z = 2$, the total baryonic accretion rate from the mass growth rate of dark matter haloes is $\dot{M}_{\rm bar} \equiv 0.18 \times \dot{M}_{\rm halo} \sim 1200$~\msunyr\ \citep{Neistein08}. However, all of these baryons are expected to be shock-heated to the virial temperature of the halo ($\sim7\times10^6$~K) and the cool gas replenishment timescale is much longer than the gas depletion timescale in such halos \citep[e.g.,][]{Dekel06,Tacchella15}. Therefore, the prolific star formation in SMGs should be unsustainable; the SFR would decline with an $e$-folding timescale of only $\sim$200~Myr \citep[2\mg/SFR; e.g.,][]{Tacconi08,Bothwell12}. At such a rate, the SMGs would become red sequence galaxies in only a Gyr or 5 $e$-folding times\footnote{This is the time it would take to decrease the specific SFR (SFR/\ms) from $\sim$$10^{-9}$~Gyr$^{-1}$ for the SMGs at the observed epoch to $\sim$$10^{-11}$~Gyr$^{-1}$ for the red sequence at $z \sim 2$ \citep{Brammer09}.} \citep{Fu13}. Such a short transitional time of a significant high-redshift star-forming population helps explain the rapid build-up of the massive end of the red sequence at $z > 1$ \citep[e.g.,][]{Ilbert13}. It makes it unnecessary to invoke any additional quenching mechanisms such as galactic outflows, which can be suppressed in such massive halos \citep[e.g.,][]{Singh16}.

However, could there be enough cool gas in the circumgalactic medium (CGM) around SMGs that may fuel a prolonged starburst phase \citep[e.g.][]{Narayanan15}? The CGM of co-eval QSOs may give us a hint, because they inhabit comparably massive ($\sim$$10^{12.6}\,M_{\odot}$) halos \citep{White12}. Contrary to the expected dominance of virialized X-ray plasma, absorption line spectroscopy of a statistical sample of $z \sim 2$ projected QSO pairs reveals the prevalence of cool ($T \sim 10^4$~K), metal-enriched ($Z \geq 0.1 Z_\odot$), and optically thick \lya\ absorbers ($N_{\rm HI} \geq 1.6\times10^{17}$~\cmsq) extending to at least the expected viral radius of 160~kpc \citep[the ``Quasar Probing Quasar'' (QPQ) project:][]{Hennawi06,Prochaska13,Prochaska13a}. The high observed covering factor of the cool CGM gas ($\gtrsim 60\%$) in $\sim$$10^{12.6}\,M_{\odot}$ halos has been compared to predictions from numerical simulations, and it has been realized that efficient star-formation-driven feedback from accreted satellite galaxies is required to increase the \HI\ covering factor to the observed level \citep[e.g.,][]{Fumagalli14,Faucher-Giguere15,Rahmati15,Faucher-Giguere16}. The models predict that the covering factor increases with halo mass and is independent of specific SFR, so SMGs are likely to show even higher \HI\ covering factors. To test this, we exploit QSO absorption line spectroscopy to probe the CGM of SMGs. We first present the data sets and the method we used to select projected \sqps\ in \S~\ref{sec:sample}. We then describe our followup observations in \S~\ref{sec:obs}, including radio interferometer imaging, near-infrared spectroscopy, and optical spectroscopy. We present our analysis and results in \S~\ref{sec:result}. Finally, we conclude by comparing the covering fraction of optically thick gas around SMGs with that of $z \sim 2$ QSOs (\S~\ref{sec:discuss}). Throughout we adopt a $\Lambda$CDM cosmology with $\Omega_{\rm m}=0.27$, $\Omega_\Lambda=0.73$ and $H_0$ = 70 km~s$^{-1}$~Mpc$^{-1}$.

@@

However, most \hers\ sources are not SMGs. To select \hers\ sources that would have been selected as SMGs if observed at 870~\um, we chose only the subsample that satisfies the following criteria: (1) $>$3$\sigma$ detections in all three SPIRE bands, (2) flux densities peak at 350~\um\ ($S_{250} < S_{350}$ and $S_{500} < S_{350}$; i.e., ``350\um\ peakers''), and (3) $S_{500} > 20$~mJy. Criterion 2 is essentially a photometric redshift selection because a typical graybody dust emission at $T = 35$~K would peak at 350~\um\ if redshifted to $z \sim 2.5\pm0.8$. In addition, the blind CO survey of the brightest 350~\um\ peakers ($S_{350} \geq 115$~mJy) has shown a strikingly similar redshift distribution as 850~\um-selected SMGs \citep{Harris12}, even though most of these bright sources are strongly lensed. Criterion 3 is introduced to ensure that the Rayleigh-Jeans extrapolation would give $S_{850} > 3$~mJy, the classic definition of an SMG, given a typical power-law slope of 3.5 (i.e., $\beta = 1.5$). Only 70,823 \hers\ sources remained after this selection, giving an average surface density of 92 per \sqdeg\ (but note that the 500~\um\ depth varies substantially from field to field).

We identified 230 projected \sqps\ with separations\footnote{$\theta_{250}$ is measured between the \hers\ position and the optical position of the QSO.} between 5\arcsec~$\leq \theta_{250} \leq$~36\arcsec\ by cross-matching the QSO and SMG subsamples described above. The corresponding impact parameters ($R_\bot$)\footnote{The impact parameter is defined as the transverse proper distance at the redshift of the foreground SMG, which equals the angular diameter distance of the SMG multiplied by the angular separation on sky ($R_\bot = D_{\rm A}(z) \times \theta$).} are between $40 < R_\bot <$~300~kpc for $z_{\rm SMG} = 2.5$. These QSO sightlines thus probe out to $\sim$1.5 virial radii of $10^{13}$~\msun\ halos ($r_{\rm vir} = 200$~kpc at $z = 2.5$). The 5\arcsec\ lower limit is imposed as an attempt to avoid FIR-bright QSOs, because the 95\%-ile positional uncertainty of the \hers\ positions is $\sim$5\arcsec. Through visual inspection of the QSO spectra, we further excluded 31 pairs whose QSOs exhibit strong broad absorption lines (BALs), have wrong redshifts, or are misclassified. Therefore, our final sample include 199 pairs, among which 90/163 QSOs have $g \leq 21/22$~AB.

\begin{figure*}[!tb]
\epsscale{1.18}
\plotone{/Users/fu/casa/15a266/figs/vla_detect.eps}
\caption{VLA 6~GHz continuum maps for the six VLA-identified SMGs. Each image is 30\arcsec$\times$30\arcsec\ centered on the \hers\ position. The restoring beam of each map is plotted as the red ellipse at the lower right corner. The white cross and the dashed white circle indicate the \hers\ positions and the 18\arcsec\ FWHM of the 250~\um\ PSF. The green square highlights the detected radio source within the \hers\ FWHM. The white diamond marks the optical position of the QSO, if it is within the displayed region. The gray dotted contour is at $-$2$\times$$\sigma$, and the black contours are at ($+$2, $+$4, $+$8)$\times$$\sigma$. Major tickmarks are spaced in 5\arcsec\ intervals. N is up and E is left for all panels.
\label{fig:detections}} 
\end{figure*}

@@

Extensive followup observations are needed to perform absorption spectroscopy of SMGs. Our first problem is that the angular resolution of \hers\ (FWHM = 18\arcsec/25\arcsec/36\arcsec\ at 250/350/500~\um) is inadequate for longslit spectroscopic observations. To obtain more accurate positions and to remove blended sources, we have to exploit interferometer observations with the Karl G. Jansky Very Large Array (VLA). Furthermore, once the positions are determined with sub-arcsec accuracy, we need to determine the spectroscopic redshifts of the SMGs with near-IR spectrographs. Finally, a high S/N optical/near-UV spectrum of the background QSO is needed to detect the UV absorption lines imprinted by the diffuse medium around the SMGs. Below we describe these observations in more details.

@@

@@

The observations were calibrated using the Common Astronomical Software Applications (CASA) package. We used the VLA pipeline to perform basic flagging and calibration. Additional flagging was performed whenever necessary by inspecting the visibility data. We used the self-calibration technique with bright sources within the primary beam to improve the calibration for four fields: HeLMS\,0015$+$0404, HeLMS\,0041$-$0410, L6-XMM\,0223$-$0605, and NGP\,1313$+$2924. For imaging and deconvolution, we used the standard CASA task {\sc clean} with ``natural'' weighting to achieve the best sensitivity. The resulting restoring beams are on average 1\farcs5$\times$1\farcs2 in FWHM and the rms noise ranges from 2.1 to 11.7~\uJy/bm (primarily driven by the different integration times).

@@

Five VLA-detected SMGs were observed with various IR spectrographs. 
%
We observed G15\,1435$+$0110, L6-FLS\,1712$+$6001, and NGP\,1333$+$2357 with the LUCI-1 spectrograph \citep{Seifert03} on the Large Binocular Telescope (LBT) on 2015 Apr 14. We used the 200 l/mm $H$+$K$ grating at $\lambda_{\rm c} = 1.93$~\um\ and the N1.8 camera (0\farcs25 per pixel) to obtain a spectral range between 1.5 and 2.3~\um. The 1\arcsec-wide 4\arcmin-long slit is centered on the VLA-determined SMG position, and the slit P.A. is chosen to obtain the QSO spectrum simultaneously. The spectral resolution ($R$) is $\sim$940 in $H$-band and $\sim$1290 in $K$-band. We obtained 32$\times$ 120~s exposures for each target. Between exposures, we dithered along the slit among six dithering positions distributed within 40\arcsec. 
%Atmospheric transparency varied dramatically during the night and no telluric star was observed. So we used the telluric star observation from the previous night for an approximate telluric and flux calibration.

@@

\begin{deluxetable*}{rccccc ccccc}
\tablewidth{0pt}
\tablecaption{Redshifts and Absorption Line Measurements
\label{tab:NHI}}
\tablehead{
\colhead{Pair Name} & \colhead{SMG} & \colhead{$z_{\rm SMG}$} & \colhead{log($L_{\rm IR}$)} & \colhead{$q_{\rm IR}$}  & \colhead{QSO} & \colhead{$z_{\rm QSO}$} & \colhead{$\theta_{\rm 6GHz}$} & 
\colhead{$R_\bot$} &  \colhead{$W_{\rm Ly\alpha}$} & \colhead{flag} \\
\colhead{} & \colhead{(J2000)} & \colhead{}  & \colhead{(\lsun)} & \colhead{} &  \colhead{(J2000)} & \colhead{} & \colhead{(\arcsec)} & \colhead{(kpc)} & \colhead{(\AA)} & \colhead{} %\\
%\colhead{(1)} & \colhead{(2)} & \colhead{(3)} & \colhead{(4)} & \colhead{(5)} & \colhead{(6)} & \colhead{(7)} &  \colhead{(8)} & \colhead{(9)}
}
\startdata
\input{/Users/fu/casa/15a266/figs/tables/table4.tex}
\enddata
%\tablecomments{
%}
\end{deluxetable*}

\begin{figure*}[!tb]
\epsscale{0.38}
\plotone{/Users/fu/data/qph_opt/lris/plot/HeLMS_0015+0404_abs2.eps}
\plotone{/Users/fu/data/qph_opt/lris/plot/NGP_1333+2357_abs2.eps}
\plotone{/Users/fu/data/qph_opt/lris/plot/L6-FLS_1712+6001_abs2.eps}
\caption{Absorption line velocity profiles for \lya, \CII\,$\lambda$1335, and \SiIV\,$\lambda\lambda$1394,1403. The Keck/LRIS spectra of the background QSOs have been normalized by a model of the QSO continuum. All panels show the region $\pm$3000~\kms\ around the systemic redshifts of the SMGs. The top panels show Gaussian fits to the \lya\ absorption line. The vertical dashed line shows the centroid velocity.
\label{fig:abs}} 
\end{figure*}

@@

We obtained deep near-IR spectra for the five VLA-detected SMGs whose spectroscopic redshifts are unknown. We detected \Ha\ and \NII\ lines from three of the five sources, enabling accurate determination of the spectroscopic redshifts (Fig.~\ref{fig:smgspec}). The two remaining sources, G15\,1413+0058 and G15\,1435+0110, show near-IR continuum emission with neither emission lines nor stellar absorption features. It is possible that the emission lines either fall into one of the telluric absorption bands or are simply outside of the spectral range. Our redshift success rate is thus 60\%, comparable to previous redshift surveys of SMGs \citep[e.g.,][]{Chapman05}. Atmosphere transparency varied substantially during the observations, so we do not have reliable flux measurements for the emission lines.

With the photometry from \hers\ and the VLA and spectroscopic redshifts, we can estimate the total rest-frame 8$-$1000~\um\ luminosity ($L_{\rm IR}$) and the IR-to-radio luminosity ratio ($q_{\rm IR}$). From the best-fit graybody models (where we fixed $\beta = 1.5$), we find that they are all Ultra-Luminous IR Galaxies (ULIRGs) with SFR$_{\rm IR}$ = 470-1500~\msunyr, when $L_{\rm IR}$ are converted to SFR using the calibration of \citet{Murphy11} for a \citet{Kroupa02} initial mass function:
\begin{equation}
 {\rm SFR}/M_{\odot}~{\rm yr}^{-1} = 1.5\times10^{-10}~L_{\rm IR}/L_{\odot}
\end{equation} 
The extrapolated 850~\um\ flux densities range between $7 \leq S_{850} \leq 18$~mJy, confirming that they are {\it bona fide} SMGs.

>>>>

\begin{abstract}
Submillimeter galaxies (SMGs) are dusty starbursts in the early universe that may have evolved into massive ellipticals today. The physical state of the circumgalactic medium of SMGs carries key information to decode massive galaxy formation yet are unexplored observationally. We exploit QSO absorption spectroscopy to probe the diffuse gas around SMGs.
% 
We first compile a sample of \sqps\ with angular separations less than 35\arcsec\ from \hers\ surveys. We then use the Very Large Array (VLA) to determine the positions of the \hers\ sources. Finally, we use near-infrared spectrographs to determine the redshifts of the five VLA-detected SMGs and optical spectrographs to obtain their QSO absorption spectra. 
%
Our survey yielded three \sqps\ with secure redshift identification for both components. The QSO sightlines probe transverse proper distances between 110 and 200~kpc. We detect strong \HI\ \lya\ absorption with rest-frame equivalent widths $W_{\rm Ly\alpha} = 1.7-2.0$~\AA\ around all three SMGs. One of the \lya\ system shows only 40\% absorption at the line center, so it is clearly optically thin (${\rm log}(N_{\rm HI}) < 17$~\cmsq) and the high $W_{\rm Ly\alpha}$ is due to line-blending. The high equivalent widths and the line center depths of the other two systems are consistent with optically thick absorbers with $18 < {\rm log}(N_{\rm HI}) < 19$~\cmsq. However, neither are convincingly optically thick, because our spectral resolution is insufficient to reveal the damping wings of the \lya\ line and the low-ionization metal lines commonly associated with optically thick absorbers are buried in the \lya\ forest. Compared to the QSOs at $z \sim 2$, our limited sample suggest that SMGs' surrounding media have lower covering fraction of optically thick cool gas. 
\end{abstract}

@@

The first mJy-level submillimeter surveys discovered a population of high-redshift submillimeter-bright galaxies (SMGs), namely, unresolved sources with 850~\um\ flux density ($S_{850}$) greater than 3-5~mJy \citep{Smail97,Barger98,Hughes98,Eales99}. The SMGs are massive \citep[\ms\ $\sim 10^{11}$~\msun;][]{Hainline11, Michalowski12, Targett12}, metal-rich \citep[$Z \sim Z_\odot$;][]{Swinbank04}, gas-rich \citep[\mg\ $\sim 3\times10^{10}$~\msun;][]{Greve05, Tacconi08, Ivison11}, extreme star-forming systems (SFR $\gtrsim 500$~\msunyr) at a median redshift of $z \sim 2.5$ \citep{Chapman05,Wardlow11,Yun12,Smolcic12}. Two lines of evidence suggest that SMGs inhabit dark matter halos as massive as $\sim$$10^{13}$~\msun: (1) their strong clustering strength estimated from the cross-correlation function between SMGs and 3.6~\um-selected galaxies \citep[\mh $\sim 9\times10^{12}$~\msun; e.g.,][]{Hickox12}, and (2) their high stellar mass and the \ms$-$\mh\ relation from abundance matching \citep[\mh~$= 6\times10^{12}$~\msun\ for \ms~$= 10^{11}$~\msun\ at $z = 2$; e.g.,][]{Behroozi10}.

It is imperative to know how long this intense star formation would last. For $10^{13}$~\msun\ halos at $z = 2$, the total baryonic accretion rate from the mass growth rate of dark matter haloes is $\dot{M}_{\rm bar} \equiv 0.18 \times \dot{M}_{\rm halo} \sim 1200$~\msunyr\ \citep{Neistein08}. However, all of these
%% JFH There is always some cold accretion even in massive systems. So I would
%% say something less definitive, like most of these baryons or a high fraction
%% of these baryosn etc, i.e. ``In such massive DM halos, it is expected
%% that most of the baryosn will be shock-heated to the virial temperature
%% of hte halo ~ 10^7 K (not your number 7e6 is low for a 10^13 Msun halo, and
%% is more appropriate for 1e12)
baryons are expected to be shock-heated to the virial temperature of the halo ($\sim7\times10^6$~K) and the cool gas replenishment timescale is much longer than the gas depletion timescale in such halos \citep[e.g.,][]{Dekel06,Tacchella15}. Therefore, the prolific star formation in SMGs should be unsustainable; the SFR would decline with an $e$-folding timescale of only $\sim$200~Myr \citep[2\mg/SFR; e.g.,][]{Tacconi08,Bothwell12}. At such a rate, the SMGs would become red sequence galaxies in only a Gyr or 5 $e$-folding times\footnote{This is the time it would take to decrease the specific SFR (SFR/\ms) from $\sim$$10^{-9}$~Gyr$^{-1}$ for the SMGs at the observed epoch to $\sim$$10^{-11}$~Gyr$^{-1}$ for the red sequence at $z \sim 2$ \citep{Brammer09}.} \citep{Fu13}. Such a short transitional time of a significant high-redshift star-forming population
%% JFH I have less faith in these models than you. I would say ``such a short
%% transitional time ... might help explain....''
helps explain the rapid build-up of the massive end of the red sequence at $z > 1$ \citep[e.g.,][]{Ilbert13}. It makes it unnecessary to invoke any additional quenching mechanisms such as galactic outflows, which can be suppressed in such massive halos \citep[e.g.,][]{Singh16}.

However, could there be enough cool gas in the circumgalactic medium (CGM) around SMGs that may fuel a prolonged starburst phase \citep[e.g.][]{Narayanan15}? The CGM of co-eval QSOs may give us a hint, because they inhabit comparably massive ($\sim$$10^{12.6}\,M_{\odot}$) halos \citep{White12}. Contrary to the expected dominance of virialized X-ray plasma, absorption line spectroscopy of a statistical sample of $z \sim 2$ projected QSO pairs reveals the prevalence of cool ($T \sim 10^4$~K), metal-enriched ($Z \geq 0.1 Z_\odot$), and optically thick \lya\ absorbers ($N_{\rm HI} \geq 1.6\times10^{17}$~\cmsq) extending to at least the expected virial radius of 160~kpc \citep[the ``Quasar Probing Quasar'' (QPQ) project:][]{Hennawi06,Prochaska13,Prochaska13a}. The high observed covering factor of the cool CGM gas ($\gtrsim 60\%$) in $\sim$$10^{12.6}\,M_{\odot}$ halos
%% JFH You are citing the wrong paper here for QPQ1, i.e. it is
%% Hennawi, Prochaska, Burles et al., not the 2006 paper on binary
%% quasars. I would also appreciate a citation to QPQ2, i.e. Hennawi
%% and Prochaska 2007 where we showed explicitly that cool gas is strongly
%% clustered around QSOs. 
has been compared to predictions from numerical simulations, and it has been realized that efficient star-formation-driven feedback from accreted satellite galaxies is required to increase the \HI\ covering factor to the observed level \citep[e.g.,][]{Fumagalli14,Faucher-Giguere15,Rahmati15,Faucher-Giguere16}.
%% JFH The situation here is more nuanced with the theory. Fumgalli et al. 2014
%% and FG15 found that current simulations cannot explain the high covering
%% factor of optically thick gas around QSOs. Rahmati found that he could
%% explain it, but he made very optimistic (and erroneous) assumptions
%% about the masses of halos populated by QSOs. FG16 found that he can
%% only match the results with high-resolution simualtions that resolve
%% feedback from small galaxies, and notably, Rahmatic has nowhere near
%% this resolution. Anyway, I'd say that ``While several studies
%% found that they cannot reproduce the high covering factor around
%% quasars (Fumgalli14, FG15, but see Rahmatic), it has been
%% argued that efficient star-formation-driven feedback from accreted
%% satellite galaxies is required to increase the \HI\ covering factor to
%% the observed level which is only resolved in the highest resolution
%% cosmological zoom simulations (FG16). 
The models predict that the covering factor increases with halo mass and is independent of specific SFR, so SMGs are likely to show even higher \HI\ covering factors. To test this, we exploit QSO absorption line spectroscopy to probe the CGM of SMGs. We first present the data sets and the method we used to select projected \sqps\ in \S~\ref{sec:sample}. We then describe our followup observations in \S~\ref{sec:obs}, including radio interferometer imaging, near-infrared spectroscopy, and optical spectroscopy. We present our analysis and results in \S~\ref{sec:result}. Finally, we conclude by comparing the covering fraction of optically thick gas around SMGs with that of $z \sim 2$ QSOs (\S~\ref{sec:discuss}). Throughout we adopt a $\Lambda$CDM cosmology with $\Omega_{\rm m}=0.27$, $\Omega_\Lambda=0.73$ and $H_0$ = 70 km~s$^{-1}$~Mpc$^{-1}$.

@@

%% JFH Would be useful to quote rough numbers for the # QSOs per deg^2 roughly
%% (I think BOSS is about 20 per deg^2, and the number of SMGs per deg^2
%%

However, most \hers\ sources are not SMGs. To select \hers\ sources that would have been selected as SMGs if observed at 870~\um, we chose only the subsample that satisfies the following criteria: (1) $>$3$\sigma$ detections in all three SPIRE bands, (2) flux densities peak at 350~\um\ ($S_{250} < S_{350}$ and $S_{500} < S_{350}$; i.e., ``350\um\ peakers''), and (3) $S_{500} > 20$~mJy. Criterion 2 is essentially a photometric redshift selection because a typical graybody dust emission at $T = 35$~K would peak at 350~\um\ if redshifted to $z \sim 2.5\pm0.8$. In addition, the blind CO survey of the brightest 350~\um\ peakers ($S_{350} \geq 115$~mJy) has shown a strikingly similar redshift distribution as 850~\um-selected SMGs \citep{Harris12}, even though most of these bright sources are strongly lensed. Criterion 3 is introduced to ensure that the Rayleigh-Jeans extrapolation would give $S_{850} > 3$~mJy, the classic definition of an SMG, given a typical power-law slope of 3.5 for a modified blackbody with a frequency-dependent absorption cross section ($\kappa \propto \nu^{1.5}$). Only 70,823 \hers\ sources remained after this selection, giving an average surface density of 92 per \sqdeg, which is consistent with the observed 870~\um\ source count function above $S_{870} \gtrsim 3$~mJy \citep{Weis09,Coppin06}. %; but note that the 500~\um\ depth varies substantially from field to field.

We identified 230 projected \sqps\ with separations\footnote{$\theta_{250}$ is measured between the \hers\ position and the optical position of the QSO.} between 5\arcsec~$\leq \theta_{250} \leq$~36\arcsec\ by cross-matching the QSO and SMG subsamples described above. The corresponding impact parameters ($R_\bot$)\footnote{The impact parameter is defined as the transverse proper distance at the redshift of the foreground SMG, which equals the angular diameter distance of the SMG multiplied by the angular separation on sky ($R_\bot = D_{\rm A}(z) \times \theta$).} are between $40 < R_\bot <$~300~kpc for $z_{\rm SMG} = 2.5$. These QSO sightlines thus probe out to $\sim$1.5 virial radii of $10^{13}$~\msun\ halos ($r_{\rm vir} = 200$~kpc at $z = 2.5$). The 5\arcsec\ lower limit is imposed as an attempt to avoid FIR-bright QSOs, because the 95\%-ile positional uncertainty of the \hers\ positions is $\sim$5\arcsec. Through visual inspection of the QSO spectra, we further excluded 31 pairs whose QSOs exhibit strong broad absorption lines (BALs),
%%JFH add parenthetically that this makes them unsuitable for absorption line
%% work. 
have wrong redshifts, or are misclassified. Therefore, our final sample include 199 pairs, among which 90/163 QSOs have SDSS $g \leq 21/22$.

\begin{figure*}[!tb]
\epsscale{1.18}
\plotone{/Users/fu/casa/15a266/figs/vla_detect2.eps}
\caption{VLA 6~GHz continuum maps for the six VLA-identified SMGs. Each image is 30\arcsec$\times$30\arcsec\ centered on the \hers\ position. The restoring beam of each map is plotted as the red ellipse at the lower right corner. The cross and the dashed circle indicate the \hers\ positions and the 18\arcsec\ FWHM of the 250~\um\ PSF. The red square highlights the detected radio source within the \hers\ FWHM. The blue diamond marks the optical position of the QSO, if it is within the displayed region. The contours are at ($+$2, $+$4)$\times$$\sigma$. Major tickmarks are spaced in 5\arcsec\ intervals. N is up and E is left for all panels.
\label{fig:detections}} 
\end{figure*}

@@

Extensive followup observations are needed to perform absorption spectroscopy of SMGs. Our first problem is that the angular resolution of \hers\ (FWHM = 18\arcsec/25\arcsec/36\arcsec\ at 250/350/500~\um) is inadequate for longslit spectroscopic observations.
%% JFH Clarify this. Explain first that the CGM analysis requires a precise redshift
%% for the foreground SMG. However the 5'' final positional uncertainity of the
%% Herschel positions precludes longslit spectroscopic observations with typical
%% slit width ~ 1.0'
To obtain more accurate positions and to remove blended sources, we exploit interferometer observations of 15 \sqps\ with the Karl G. Jansky Very Large Array (VLA). Furthermore, once the positions are determined with sub-arcsec accuracy, we need to determine the spectroscopic redshifts of the SMGs with near-IR spectrographs.
%% JFH Maybe clarify that success rate is much higher in near-IR for the SMGs. 
Finally, a high S/N optical/near-UV spectrum of the background QSO is needed to detect the UV absorption lines imprinted by the diffuse medium around the SMGs. Below we describe these observations in more details.

@@

%% JFH State the zeroth order idea here, i.e. we get better positions
%% using the faint radio continuum, where the emission is synchrotron emission
%% from shocked gas in massive star winds, etc. according to FIR-radio correlation
%% etc. etc.

@@

The observations were calibrated using the Common Astronomical Software Applications (CASA) package. We used the VLA pipeline to perform basic flagging and calibration. Additional flagging was performed whenever necessary by inspecting the visibility data. We used the self-calibration technique with bright sources within the primary beam to improve the calibration for four fields: HeLMS\,0015$+$0404, HeLMS\,0041$-$0410, L6-XMM\,0223$-$0605, and NGP\,1313$+$2924. For imaging and deconvolution, we used the standard CASA task {\sc clean} with ``natural'' weighting to achieve the best sensitivity. The resulting restoring beams are on average 1\farcs5$\times$1\farcs2 in FWHM and the rms noise ranges from 2.1 to 14.1~\uJy/bm with a mean at 6~\uJy/bm. The variation in rms is primarily driven by systematic noise (e.g., confusion sources). The different integration times play a minor role.

%% JFH Quote a number for the final positional accuracy of the VLA data
%% for a typical case i.e. S/N.

%% JFH I guess Figure 1 should be reference in this section but it is not.

@@

Five VLA-detected SMGs were observed with various IR spectrographs. 
%
We observed G15\,1435$+$0110, L6-FLS\,1712$+$6001, and NGP\,1333$+$2357 with the LUCI-1
%% JFH Spell out instrument acronym on first usage. 
spectrograph \citep{Seifert03} on the Large Binocular Telescope (LBT) on 2015 Apr 14. We used the 200 l/mm $H$+$K$ grating at $\lambda_{\rm c} = 1.93$~\um\ and the N1.8 camera (0\farcs25 per pixel) to obtain a spectral range between 1.5 and 2.3~\um. The 1\arcsec-wide 4\arcmin-long slit is centered on the VLA-determined SMG position, and the slit P.A. is chosen to obtain the QSO spectrum simultaneously. The spectral resolution ($R$) is $\sim$940 in $H$-band and $\sim$1290 in $K$-band. We obtained 32$\times$ 120~s exposures for each target. Between exposures, we dithered along the slit among six dithering positions distributed within 40\arcsec. 
%Atmospheric transparency varied dramatically during the night and no telluric star was observed. So we used the telluric star observation from the previous night for an approximate telluric and flux calibration.

@@

%% JFH So in this Table, I'd suggest changing ``flag'' to ``classification'' 
\begin{deluxetable*}{rccccc ccccc}
\tablewidth{0pt}
\tablecaption{Redshifts and Absorption Line Measurements
\label{tab:NHI}}
\tablehead{
\colhead{Pair Name} & \colhead{SMG} & \colhead{$z_{\rm SMG}$} & \colhead{log($L_{\rm IR}$)} & \colhead{$q_{\rm IR}$}  & \colhead{QSO} & \colhead{$z_{\rm QSO}$} & \colhead{$\theta_{\rm 6GHz}$} & 
\colhead{$R_\bot$} &  \colhead{$W_{\rm Ly\alpha}$} & \colhead{flag} \\
\colhead{} & \colhead{(J2000)} & \colhead{}  & \colhead{(\lsun)} & \colhead{} &  \colhead{(J2000)} & \colhead{} & \colhead{(\arcsec)} & \colhead{(kpc)} & \colhead{(\AA)} & \colhead{} %\\
%\colhead{(1)} & \colhead{(2)} & \colhead{(3)} & \colhead{(4)} & \colhead{(5)} & \colhead{(6)} & \colhead{(7)} &  \colhead{(8)} & \colhead{(9)}
}
\startdata
\input{/Users/fu/casa/15a266/figs/tables/table4.tex}
\enddata
%\tablecomments{
%}
\end{deluxetable*}

\begin{figure*}[!tb]
\epsscale{0.38}
\plotone{/Users/fu/data/qph_opt/lris/plot/HeLMS_0015+0404_abs2.eps}
\plotone{/Users/fu/data/qph_opt/lris/plot/NGP_1333+2357_abs2.eps}
\plotone{/Users/fu/data/qph_opt/lris/plot/L6-FLS_1712+6001_abs2.eps}
\caption{Absorption line velocity profiles for \lya, \CII\,$\lambda$1335, and \SiIV\,$\lambda\lambda$1394,1403. The Keck/LRIS spectra of the background QSOs have been normalized by a model of the QSO continuum. All panels show the region $\pm$3000~\kms\ around the systemic redshifts of the foreground
%% JFH I added foreground here. 
  SMGs. The top panels show Gaussian fits to the \lya\ absorption line. The vertical dashed line shows the centroid velocity.
\label{fig:abs}} 
\end{figure*}

@@

We obtained deep near-IR spectra for the five VLA-detected SMGs whose spectroscopic redshifts are unknown. We detected \Ha\ and \NII\ lines from three of the five sources, enabling accurate determination of the spectroscopic redshifts (Fig.~\ref{fig:smgspec}). The two remaining sources, G15\,1413+0058 and G15\,1435+0110, show near-IR continuum emission with neither emission lines nor stellar absorption features. It is possible that the emission lines either fall into one of the telluric absorption bands or are simply outside of the spectral range.
%% JFH I would advocate that you should show what these spectra look like for the
%% failures. 
Our redshift success rate is thus 60\%, comparable to previous redshift surveys of SMGs \citep[e.g.,][]{Chapman05}. Atmosphere transparency varied substantially during the observations, so we do not have reliable flux measurements for the emission lines.
%% JFH Why can't we use the telluric standards for this flux calibration??

%% JFH I'm not sure I believe Figure 2 L6-FLS. I think in the upper panel, you
%% should be plotting the chi-map, i.e. chi = (data - sky_model)/noise. It is
%% much easier to convince yourself that a line detection is real in such a map,
%% since things inconsistent with the background will be high n-sigma peaks.
